\subsection{Thermodynamics and Kinetics}

\subsubsection{Explain different types of combustion.}

{\color{gray}\footnotesize [Claude context: check Lecture 4 (Basics of Flames -- classification of combustion/flame types); Maas notes Ch.1 / Warnatz Ch.1 (Fundamental Definitions and Phenomena)]}

\paragraph{Answer}
\textbf{Fuel and ox mix:} Non Premix and premix. \textbf{Flow Nature:} Laminar or Turbulent. \textbf{Phase of reactants:} Homogeneous and Non Homogeneous \textbf{Temporal variation:} Steady or Unsteady.  \textbf{Mode of Combustion:} Propagation or Explosion. \textbf{Speed of flow:} Compressible or incomprehensible. 



\subsubsection{Explain the different types of enthalpies and how to determine the enthalpy of a reaction.}

{\color{gray}\footnotesize [Claude context: check Lecture 2 (Thermodynamics \& Chemical Equilibrium); Maas notes Ch.4 / Warnatz Ch.4 (Thermodynamics of Combustion Processes); Lecture Notes L1\&2]}

\paragraph{Answer}
Lecture 1 is more useful: Enthalpy of formation, is the neergy needed to form 1kg of a species at 298.15K. 

It is impossible to define an absolute quantity ofr enthalpy, therefore they are relative quantities. The standard temperature of 298 K was chosen in preference to the 0K because of experimental dificulties with the later. To measure this quantities a Bomb calomiter is used. In thi standard pure elemnts are considered to have 0 enthalpy of formation. Experimentaly it is possible to determine the energy released or added to form other compounds. Hess Law states




\subsubsection{What is heat capacity and why does it vary?}

{\color{gray}\footnotesize [Claude context: check Lecture 2 (Thermodynamics \& Chemical Equilibrium); Thermodynamics Recap audioslides (heat capacity, variation with T); Maas notes Ch.4 / Warnatz Ch.4]}

\paragraph{Answer}




\subsubsection{What is adiabatic flame temperature and how does it vary with parameters like equivalence ratio, inlet temperature, pressure, fuel type, etc.?}

{\color{gray}\footnotesize [Claude context: check Lecture 2 (adiabatic flame temperature, equivalence ratio, pressure/temperature effects); Maas notes Ch.4 / Warnatz Ch.4]}

\paragraph{Answer}




\subsubsection{What is Gibbs energy and how does it define spontaneity?}

{\color{gray}\footnotesize [Claude context: check Lecture 2 (chemical equilibrium and free energy); Thermodynamics Recap audioslides (second law, entropy); Maas notes Ch.4 / Warnatz Ch.4]}

\paragraph{Answer}



