\subsection{Laminar Transport}

\subsubsection{In steady state combustion studies, enthalpy $h$ is often chosen as the energy variable. What is the relation between enthalpy and temperature? Explain the physical meaning of the different terms in the equation for enthalpy (equation will be given). Explain the physical meaning of the different terms in the equation for temperature (equation will be given).}

{\color{gray}\footnotesize [Claude context: check Lecture 8 (Laminar and Turbulent Transport Processes -- conservation equations, energy/enthalpy formulation); Kuo Ch.3 (sec.\ 1-2, 4, 11, conservation equations for reacting flows); Maas notes Ch.3 / Warnatz Ch.3 \& Ch.12]}

\paragraph{Answer}


Enthalpy is a measure of internal energy; temperature is one of the forms in which internal energy is expressed. Total temperature is related to enthalpy through $c_p$, which also corresponds to enthalpy for isobaric or constant-volume systems.

Enthalpy considers internal energy, kinetic energy, and pressure.

The conservation equation considers the change in time, density variation/transport, as well as convective flux, diffusive heat transfer, fluid stress, the Dufour effect, and the gradient in species mass concentration.

\todo{what is the temp equation?}

{\color{istblue}
\paragraph{Claude answer}
The \textbf{relation between enthalpy and temperature} runs through the caloric equation of state. For each species, the absolute (total) specific enthalpy is $h_i(T) = \Delta h_{f,i}^0 + \int_{T_0}^{T} c_{p,i}(T')\,dT'$, i.e.\ the sum of a \textbf{chemical part} (formation enthalpy) and a \textbf{thermal (sensible) part}; for the mixture, $h = \sum_i Y_i h_i$. Temperature is therefore not proportional to enthalpy in a reacting flow: $dh = c_p\,dT$ holds only at \textbf{frozen composition}. During reaction the mass fractions change, converting chemical into sensible enthalpy at constant $h$ --- which is exactly why $h$ is a convenient variable: in a steady, adiabatic, isobaric (low-Mach) flame the total enthalpy is conserved ($h_b = h_u$), it has \textbf{no chemical source term}, and given $h$, $p$ and the composition, $T$ follows by inverting the caloric relation~\cite{lecture8,maas_combustion_lecture}.

\textbf{Enthalpy equation.} Under the standard flame assumptions (low Mach number so kinetic energy and viscous heating are negligible, constant pressure, no gravity, no radiation), the conservation equation for the mixture enthalpy reads~\cite{kuo2005conservation,lecture8}
\begin{equation*}
\frac{\partial (\rho h)}{\partial t} + \nabla \cdot (\rho \vec{v}\, h) = -\nabla \cdot \vec{q}, \qquad
\vec{q} = -\lambda \nabla T + \rho \sum_i h_i Y_i \vec{V}_i + \vec{q}_{\mathrm{Dufour}}.
\end{equation*}
The terms mean: \textbf{(i)} local accumulation of enthalpy in time (unsteady term); \textbf{(ii)} \textbf{convective flux}, transport of enthalpy by the mass-averaged mixture velocity $\vec{v}$; \textbf{(iii)} divergence of the \textbf{diffusive energy flux} $\vec{q}$, itself composed of: heat \textbf{conduction} down the temperature gradient (\textbf{Fourier's law}, $-\lambda \nabla T$); transport of enthalpy by \textbf{species diffusion}, since each species carries its own enthalpy $h_i$ while diffusing with velocity $\vec{V}_i$ relative to the mixture (important when species diffuse at different rates, i.e.\ non-unity Lewis numbers); and the \textbf{Dufour effect}, a heat flux driven by species concentration gradients, which is almost always negligible. In the general (compressible) formulation additional terms appear: the pressure work $Dp/Dt$ (vanishes for steady isobaric flow), viscous dissipation $\Phi$ (negligible at low Mach), body-force work and radiation~\cite{warnatz2006combustion,kuo2005conservation}. Note that \textbf{no reaction source term} appears: heat release is an internal conversion of chemical into sensible enthalpy, invisible to the total enthalpy.

\textbf{Temperature equation.} Substituting $h_i = \Delta h_{f,i}^0 + \int c_{p,i}\,dT$ and using the species equations, the same energy balance written for $T$ becomes (1-D form of Maas Ch.\,3~\cite{maas_combustion_lecture})
\begin{equation*}
\rho c_p \frac{\partial T}{\partial t} = \frac{\partial}{\partial z}\!\left(\lambda \frac{\partial T}{\partial z}\right) - \Big(\rho v c_p + \sum_i j_i c_{p,i}\Big)\frac{\partial T}{\partial z} \;-\; \sum_i h_i r_i .
\end{equation*}
Term by term: $\rho c_p\, \partial T/\partial t$ is the \textbf{accumulation} of sensible energy; the first RHS term is \textbf{heat conduction}; the second groups \textbf{convection} by the mixture flow ($\rho v c_p$) with the transport of sensible heat by the \textbf{species diffusion fluxes} $j_i = \rho Y_i V_i$, each weighted by its own $c_{p,i}$; and $-\sum_i h_i r_i$ is the \textbf{chemical heat-release source} ($r_i$ = chemical production rate of species $i$), which is positive for exothermic reaction since consumed reactants have higher formation enthalpy than the products formed. The key contrast with the enthalpy equation is that the strongly non-linear reaction source appears \textbf{explicitly} in the $T$-equation, while in the $h$-equation it is absorbed in the definition of $h$ --- the main reason $h$ is preferred as the energy variable in steady combustion studies.
}


\subsubsection{Transport of momentum due to viscosity is analogous to transport of heat by conduction and is analogous to transport of species by diffusion. Explain this and introduce relevant dimensionless numbers.}

{\color{gray}\footnotesize [Claude context: check Lecture 8 (species diffusion models, transport analogies); Kuo Ch.3 (sec.\ 1-2, 4, 11); Maas notes Ch.3 / Warnatz Ch.3 (Pr, Sc, Le numbers)]}

\paragraph{Answer}


They depend on a gradient.

The Lewis number is the ratio of thermal diffusivity to the mass diffusivity of the species.

\todo{Elaborate more on this}

{\color{istblue}
\paragraph{Claude answer}
All three transport processes share the same molecular mechanism and hence the same mathematical structure: random molecular motion carries a property (mass of a species, momentum, thermal energy) from regions of high to low concentration of that property, producing a \textbf{diffusive flux proportional to the local gradient} and directed against it, so that gradients are always smoothed out. Writing the fluxes in one dimension (constant density form)~\cite{lecture8}:
\begin{align*}
\text{species mass (\textbf{Fick}):} \quad & J_{i,x} = -D_i^M\, \frac{\partial (\rho Y_i)}{\partial x}, \\
\text{momentum (\textbf{Newton}):} \quad & \tau_{xy} = -\nu\, \frac{\partial (\rho v_y)}{\partial x}, \\
\text{heat (\textbf{Fourier}):} \quad & q_x = -\alpha\, \frac{\partial (\rho c_p T)}{\partial x}, \qquad \alpha \equiv \frac{\lambda}{\rho c_p}.
\end{align*}
The proportionality constants --- the species diffusivity $D_i^M$, the kinematic viscosity $\nu = \mu/\rho$, and the thermal diffusivity $\alpha$ --- all have the \textbf{same units} $\mathrm{m^2/s}$, which makes the analogy quantitative: each measures how fast the corresponding property spreads in space (a diffusive layer grows as $\sqrt{D t}$). They are material properties depending on temperature, pressure and composition. The analogy is not exact in general mixtures (Fick's law is strictly valid for binary mixtures or a dilute species in an abundant carrier; cross effects such as Soret/Dufour exist~\cite{warnatz2006combustion,kuo2005conservation}), but it underpins all simplified transport modelling in combustion.

The pairwise ratios of these diffusivities give the relevant \textbf{dimensionless numbers}:
\begin{equation*}
\mathrm{Sc}_i = \frac{\nu}{D_i^M}, \qquad \mathrm{Pr} = \frac{\nu}{\alpha}, \qquad \mathrm{Le}_i = \frac{\alpha}{D_i^M} = \frac{\mathrm{Sc}_i}{\mathrm{Pr}}.
\end{equation*}
The \textbf{Schmidt number} compares momentum to species diffusion, the \textbf{Prandtl number} momentum to heat diffusion (a pure fluid property, $\approx 0.7$ for air), and the \textbf{Lewis number} heat to species diffusion. The Lewis number is the most important one for flames: it compares how fast heat diffuses out of the reaction zone with how fast the reactant diffuses in. A common model is \textbf{constant Lewis numbers}, computing $D_i^M = \alpha/\mathrm{Le}_i$, and the simplest closure is $\mathrm{Le}_i = 1$ for all species, for which species and temperature profiles become similar and the mixture enthalpy is uniform through a flat flame. This is reasonable for \ce{CH4} ($\mathrm{Le} \approx 0.97$), \ce{N2} (1.00) or \ce{O2} (1.11), but fails badly for light species: $\mathrm{Le}_{\ce{H2}} \approx 0.3$ and $\mathrm{Le}_{\ce{H}} \approx 0.18$~\cite{lecture8,turns2000introduction}. Such \textbf{preferential (differential) diffusion} means hydrogen diffuses ahead of heat into the preheat zone (its mole fraction changes upstream of the temperature rise, producing e.g.\ a local maximum in the \ce{O2} profile of a flat \ce{H2} flame~\cite{warnatz2006combustion}), locally modifying the equivalence ratio and burning intensity --- the origin of thermo-diffusive instabilities and cellular burning in lean hydrogen flames~\cite{day2009cellular}.
}
