\subsection{Turbulent Transport}

\subsubsection{What are relevant physical time scales in turbulent flow? How do they relate to chemical time scales?}

{\color{gray}\footnotesize [Claude context: check Lecture 10 (Turbulence-Chemistry Interaction \& Modelling) and Lecture 8 (how turbulence affects combustion regimes); Warnatz Ch.13 (Turbulent Reacting Flows); JMBC course chapter 8 (Roekaerts)]}

\subsubsection{Give a short description of the three main approaches to the computation of turbulent flames and specify their advantages and drawbacks.}

{\color{gray}\footnotesize [Claude context: check Lecture 10 (overview of combustion models -- PDF methods, flamelet models, mean reaction rates); Warnatz Ch.13; combustion\_modeling.pdf (Veynante \& Vervisch review, used as supplementary, verify against Warnatz)]}

\subsubsection{Explain the main closure problems that arise when averaging the transport equations for an exothermic reacting flow.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (Turbulent Reacting Flows); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\subsubsection{Density-weighted averaging, also called Favre averaging, is an alternative way of averaging leading to a specific form of the averaged transport equations. What is Favre averaging? What is this specific form? Can it be expected to be a good approach for premixed flames / for non-premixed flames?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (Favre/density-weighted averaging); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\subsubsection{Explain what is meant by Large Eddy Simulation of turbulent flow. Also discuss the need for subgrid models of combustion processes in the context of LES.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (LES, subgrid closures); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}
