\subsection{Premixed Combustion}

\subsubsection{Discuss the structure of a flat laminar premixed flame.}

{\color{gray}\footnotesize [Claude context: check Lecture 9 (Laminar and Turbulent Flames); Maas notes Ch.7.1, 7.2, 7.4 / Warnatz Ch.3 \& Ch.7 (Mathematical Description / Laminar Premixed Flames)]}

\paragraph{Answer}

little rise in temperature while breakdown of fuel and oxidizer is happening.  

Thin reaction zone with sudden rise in temperature. Radiacsl combine. 

Follow up one has littel reactions, is mostly oxidations and slow reactions





\subsubsection{Discuss the classical regime diagrams of turbulent premixed combustion (Borghi and Peters diagrams).}

{\color{gray}\footnotesize [Claude context: check Lecture 9; Warnatz Ch.15 (Turbulent Premixed Flames); JMBC course chapter 8 (Roekaerts, supplementary, verify against Warnatz)]}

\paragraph{Answer}

exlaines in \ref{Q:tiemscales}



\todo{To calude: reference the previus section as well ,do not repeat information but u may add whaever u think is needed}

\subsubsection{What is laminar flame speed? What is turbulent flame speed? How are they related?}

{\color{gray}\footnotesize [Claude context: check Lecture 9; Maas notes Ch.7 / Warnatz Ch.8.3 (Flame velocities) \& Ch.15]}

\paragraph{Answer}




\subsubsection{What is turbulent flame speed closure?}

{\color{gray}\footnotesize [Claude context: check Lecture 9/10; Warnatz Ch.15 (Turbulent Premixed Flames); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}




\subsubsection{How can a laminar premixed flame be described in an intrinsic way using a so-called progress variable? How can a turbulent premixed flame be described using a progress variable?}

{\color{gray}\footnotesize [Claude context: check Lecture 9/10; Warnatz Ch.15 (progress variable, premixed turbulent combustion); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}



