\subsection{Non-Premixed Combustion}

\subsubsection{What is the typical structure of a laminar diffusion flame?}

{\color{gray}\footnotesize [Claude context: check Lecture 9 (Laminar and Turbulent Flames); Maas notes Ch.13.1, 13.3, 13.4 / Warnatz Ch.13 (Nonpremixed Flames)]}

\paragraph{Answer}




\subsubsection{Why is there no such thing as a laminar flame speed of a diffusion flame?}

{\color{gray}\footnotesize [Claude context: check Lecture 9; Maas notes Ch.13 / Warnatz Ch.13 (Nonpremixed Flames)]}

\paragraph{Answer}




\subsubsection{Define mixture fraction. Which conditions have to be satisfied in order that mixture fraction becomes a useful variable? Explain the idea that, using mixture fraction, a non-premixed flame problem can be split into a mixing problem and a chemical problem.}

{\color{gray}\footnotesize [Claude context: check Lecture 9/10; Maas notes Ch.13 / Warnatz Ch.14 (Turbulent Non-Premixed Flames); combustion\_modeling.pdf (supplementary, verify against Warnatz/Maas)]}

\paragraph{Answer}




\subsubsection{Define mixture fraction. In which circumstances can enthalpy be considered equivalent to mixture fraction?}

{\color{gray}\footnotesize [Claude context: check Maas notes Ch.13 / Warnatz Ch.14 (Turbulent Non-Premixed Flames); Lecture 9/10]}

\paragraph{Answer}




\subsubsection{Explain how the influence of turbulent fluctuations of mixture fraction can be taken into account by making use of an assumed shape of its probability density function.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (Turbulent Non-Premixed Flames, presumed PDF approach); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}




\subsubsection{Explain why one is interested in calculating the variance of mixture fraction. How does the scalar dissipation rate influence the variance of mixture fraction?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (mixture fraction variance, scalar dissipation rate); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}




\subsubsection{Explain the steady laminar flamelet model of turbulent non-premixed combustion.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (flamelet model for non-premixed combustion); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}



