\subsection{Combustion Modelling}

\subsubsection{Give a short description of the three main approaches to the computation of turbulent flames and specify their advantages and drawbacks.}

{\color{gray}\footnotesize [Claude context: check Lecture 10 (overview of combustion models -- PDF methods, flamelet models, mean reaction rates); Warnatz Ch.13; combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}  same as \ref{Q:3aproax}



\subsubsection{Explain the main closure problems that arise when averaging the transport equations for an exothermic reacting flow.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (Turbulent Reacting Flows); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} same as \ref{Q:clouseure}




\subsubsection{Density-weighted averaging, also called Favre averaging, is an alternative way of averaging leading to a specific form of the averaged transport equations. What is Favre averaging? What is this specific form?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (Favre/density-weighted averaging); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} same as \ref{Q:density}




\subsubsection{Explain what is meant by Large Eddy Simulation of turbulent flow. Also discuss the need for subgrid models of combustion processes in the context of LES.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (LES, subgrid closures); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} same as \ref{Q:LES}




\subsubsection{Define mixture fraction. Which conditions have to be satisfied in order that mixture fraction becomes a useful variable? Explain the idea that, using mixture fraction, a non-premixed flame problem can be split into a mixing problem and a chemical problem.}

{\color{gray}\footnotesize [Claude context: check Lecture 9/10; Maas notes Ch.13 / Warnatz Ch.14 (Turbulent Non-Premixed Flames); combustion\_modeling.pdf (supplementary, verify against Warnatz/Maas)]}

\paragraph{Answer} same as \ref{Q:mixfrac}




\subsubsection{Explain the structure of the strained laminar flamelet model for non-premixed combustion.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (flamelet model, strained flames); Dynamics of Stretched Flames (Law, 1988, supplementary on flame stretch, verify against Warnatz); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} same as \ref{Q:stedylaminatflameletmodel}




\subsubsection{Explain how the influence of turbulent fluctuations of mixture fraction can be taken into account by making use of an assumed shape of its probability density function.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (presumed PDF approach); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer}

For turbulent flow, the equations have to be written in terms of a Favre average (density-weighted average). Nevertheless, the influence of turbulence still has to be taken into account. In order to determine the average influence of turbulence, a prescribed PDF is used. This PDF allows the calculation of an average through an integral, giving the determination of the average values.


similar to \ref{Q:AssumedPDF}




\subsubsection{Explain why one is interested in calculating the variance of mixture fraction. How does the scalar dissipation rate influence the variance of mixture fraction?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.14 (mixture fraction variance, scalar dissipation rate); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} similar to \ref{Q:Variance of mixure fraction}

In order to calculate the average quantity of a property, including the influence of turbulent flow and variations, a PDF is needed. Such a PDF is defined with an assumed shape, a mean and a variance. Variance is therefore important for the definition of the PDF function.

Scalar dissipation rate quantifies how much turbulence is influencing the mixture fraction gradient in dispersion. It increases the dissipation of the variance of the assumed PDF. Scalar dissipation rate plays a dissipative role in the equation for the variance.




\subsubsection{Explain how model development and experiments come together in the process of model validation. Provide some conditions for good model validation.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Lecture 5/6 (experimental methods, canonical flames); combustion\_modeling.pdf (validation against DNS/experiments, supplementary, verify against Warnatz where possible)]}

\paragraph{Answer}  Many models need empirical constants.

Experiments can determine the dependent variables.

Validation requires the same conditions.




\subsubsection{List some key characteristics of the Sandia Flame series (D-E-F).}

{\color{gray}\footnotesize [Claude context: check Lecture 10; combustion\_modeling.pdf (TNF workshop benchmark flames, supplementary -- explicitly flag as unverified against infallible sources if not covered in Warnatz/Maas)]}

\paragraph{Answer}

They are increasing in speed.






\subsubsection{Discuss the presence and importance of stretch in the counterflow flame configuration.}

{\color{gray}\footnotesize [Claude context: check Lecture 9; Dynamics of Stretched Flames (Law, 1988, supplementary -- explicitly flag as unverified against infallible sources if not covered in Warnatz/Maas); Warnatz Ch.7/Ch.13 for flame structure]}

\paragraph{Answer} The most important is tangential stretch. The tangential stretch carries the radicals outwards, possibly extinguishing the flame front.




\subsubsection{How can a laminar premixed flame be described in an intrinsic way using a so-called progress variable? How can a turbulent premixed flame be described using a progress variable?}

{\color{gray}\footnotesize [Claude context: check Lecture 9/10; Warnatz Ch.15 (progress variable, premixed turbulent combustion); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} same as \ref{Q:premix progress var}






\subsubsection{Provide an outline of the FGM approach to turbulent non-premixed combustion.}

{\color{gray}\footnotesize [Claude context: check Lecture 10; combustion\_modeling.pdf (FGM/flamelet-generated manifolds, supplementary -- explicitly flag as unverified against infallible sources if not covered in Warnatz/Maas)]}

\paragraph{Answer} Not sure what FGM is.

\todo{for Claude: still write the answer to this one}




\subsubsection{In which sense is the Transported PDF method to turbulent combustion completely different from flamelet models?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13 (PDF methods overview); combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} They are 2 different models.
Flamelet should be used when the flame is much thinner than any turbulent scale. Considering a thin reaction flame and neglecting transport in the tangential direction simplifies the simulation. In this simulation, coordinates with Z and their normal directions are used near the flame. \todo{For Claude: is this only for non-premixed? Is PDF only for premixed?}

PDF is meant for when turbulence and chemistry cannot be decoupled. Turbulence influences mixing. Turbulence requires the use of density-weighted average quantities, especially for the Arrhenius term, and the chemical source term cannot be evaluated simply from a mean quantity. To solve this, the average influence of the turbulent fluctuations is calculated from a PDF.




\subsubsection{In which cases are flamelet models recommended, and in which cases transported PDF models?}

{\color{gray}\footnotesize [Claude context: check Lecture 10; Warnatz Ch.13/Ch.14; combustion\_modeling.pdf (supplementary, verify against Warnatz)]}

\paragraph{Answer} Based on the previous answer and the Peters diagram.

Flamelets when sl > u\_rms or Ka < 1, t\_chem < t\_k. See \ref{Q: models peters}





