\subsection{Knowledge Integration and Application}

\subsubsection{Is it possible to design a burner that has a stable flame both when methane is used as a fuel and when hydrogen is used as fuel? What would be your suggestions to realize this objective and why?}

{\color{gray}\footnotesize [Claude context: check Lecture 14 (hydrogen combustion -- intrinsic instabilities, low-NOx combustor technologies, micro-mix); hydrogen\_instability.pdf (Oppong et al.\ 2022, supplementary -- explicitly flag as unverified against infallible sources if not covered in Warnatz/Maas); Maas notes Ch.7 / Warnatz Ch.7-8 for laminar flame speed/stability basics]}

\paragraph{Answer}




\subsubsection{Radiation plays a different role in the combustion process in rockets, gas turbines, and process furnaces. Explain why. How can we influence the type and amount of radiation produced by a flame?}

{\color{gray}\footnotesize [Claude context: no dedicated lecture on radiation -- check Lecture 12/13 (soot-radiation link in practical combustors); combustion.pdf (Glassman \& Yetter, supplementary -- explicitly flag as unverified against infallible sources, no direct chapter identified in Warnatz/Maas)]}

\paragraph{Answer}




\subsubsection{List possible sources of pollution from natural gas combustion.}

{\color{gray}\footnotesize [Claude context: check Lecture 12 (aircraft/combustion emissions overview) and Lecture 13 (NOx formation mechanisms)]}

\paragraph{Answer}




\subsubsection{Explain how \ce{NOx} formation via the Zel'dovich mechanism can be described.}

{\color{gray}\footnotesize [Claude context: check Lecture 13 (NOx formation mechanisms); Maas notes Ch.8.1 / Warnatz Ch.17.1 (Thermal/Zeldovich NO)]}

\paragraph{Answer}




\subsubsection{Explain how the burner design can influence thermal \ce{NOx} formation.}

{\color{gray}\footnotesize [Claude context: check Lecture 13 (combustor design parameters affecting NOx) and Lecture 14 (low-NOx combustor technologies); Maas notes Ch.8.1 / Warnatz Ch.17.1, 17.5]}

\paragraph{Answer}




\subsubsection{Explain how soot formation arises and how it could be modelled. Explain how the burner design can influence soot formation.}

{\color{gray}\footnotesize [Claude context: check Lecture 12 (soot formation mechanisms, parameters governing soot emissions) and Lecture 13 (combustor design); Warnatz Ch.18.1, 18.3 (Soot Formation Phenomenology)]}

\paragraph{Answer}



